DOpElib:\\ Differential Equations and Optimization Environment

### 2017-04-12 Examples/Documentation/introduction.tex
added full deal.ii config line to docu

A configuration of deal.II working with \texttt{DOpElib} can be obtained with
the following commands assuming that one is currently in the 
directory where the deal.II sources are located.
\begin{lstlisting}
mkdir build
cd build 
cmake -DCMAKE_INSTALL_PREFIX=/path/to/install/dir ../deal.II
make install
\end{lstlisting}
If in addition, features are desired corresponding flags need to be passed to
cmake. An excellent description is provided on the deal.II webpage
\begin{lstlisting}
http://www.dealii.org/8.5.0/readme.html
\end{lstlisting}

>>>>

A configuration of deal.II working with \texttt{DOpElib} can be obtained with
the following commands assuming that one is currently in the 
directory where the deal.II sources are located.
\begin{lstlisting}
mkdir build
cd build 
cmake -DCMAKE_INSTALL_PREFIX=/path/to/install/dir ../deal.II
make install
\end{lstlisting}
If in addition, features are desired corresponding flags need to be passed to
cmake. An excellent description is provided on the deal.II webpage
\begin{lstlisting}
http://www.dealii.org/8.5.0/readme.html
\end{lstlisting}
Currently, for all features of \texttt{DOpElib} the following settings
are useful to be passed to cmake
\begin{lstlisting}
  cmake -DCMAKE_INSTALL_PREFIX=[path to install dir] \ 
      -DDEAL_II_WITH_UMFPACK=true \
      -DDEAL_II_FORCE_BUNDLED_UMFPACK=true \
      -DDEAL_II_WITH_TRILINOS=true \
      -DTRILINOS_DIR=[path to trilinos] \
      -DDEAL_II_WITH_MPI=true \
      -DDEAL_II_WITH_P4EST=true \
      -DP4EST_DIR=[path to p4est] \
      [Path to deal.II sources]
\end{lstlisting}
